---
title: "bl_graphs"
output: html_document
date: '2022-06-21'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
```

```{r cars}
load("~/Virginia Tech/Internship 2022/2022-DSPG-LivDiv-/data/livdivdata.RData")

baseline <- livdiv %>%
  slice(1:307,)
```

```{r cars}
baseline %>%
summarise_at(c("head_edu", "head_age", "head_female", "head_married", "nb_marw", "nb_put_saving"), mean, na.rm = TRUE)

sumstats <- baseline %>%
summarise_at(c("head_edu", "head_age", "head_female", "head_married", "nb_marw", "nb_put_saving"), mean, na.rm = TRUE)

sumstats2 <- baseline %>%
  summarise_at(c("head_edu", "head_age", "head_female", "head_married", "nb_marw", "nb_put_saving"), min, na.rm = TRUE)

sumstats3 <- baseline %>%
  summarise_at(c("head_edu", "head_age", "head_female", "head_married", "nb_marw", "nb_put_saving"), max, na.rm = TRUE)

sumstats <- rbind(sumstats, sumstats2, sumstats3)

rownames <- c("Mean", "Min", "Max")
row.names(sumstats) <- rownames
```

## HH Primary Occupation 

```{r cars}
occup1 <- baseline %>% 
  filter(relationship1 == 1) %>%
  select(c(village = "village", job = "job1_1"))
occup2 <- baseline %>% 
  filter(relationship2 == 1) %>%
  select(c(village = "village", job = "job1_2"))
occup3 <- baseline %>% 
  filter(relationship3 == 1) %>%
  select(c(village = "village", job = "job1_3"))
occup4 <- baseline %>% 
  filter(relationship4 == 1) %>%
  select(c(village = "village", job = "job1_4")) 

occup1 = na.omit(occup1)
occup2 = na.omit(occup2)
occup3 = na.omit(occup3)
occup4 = na.omit(occup4)

occup <- rbind(occup1, occup2, occup3, occup4)
```


```{r cars}

```

1Agricultural wage worker
2Livestock worker
3Farmer
4Casual labor
5Construction/brick labor
6Gleaning/foraging
7Fisherman
8Fishery worker
9Factory worker
10Household help
11Transport related work
12Own business
13Service Work (NGO, gov,etc.)
14 NREGA
15Housewife
16 Other

```{r}
ggplot(occup, aes(x = job)) +
  geom_histogram() +
  bins
  scale_x_discrete(labels = c("1" = "Agricultural wage worker", "Livestock worker" = "2", "Farmer" = "3", "Casual labor" = "4", "Construction/brick labor" = "5", "Gleaning/foraging" = "6", "Fisherman" = "7", "Fishery worker" = "8", "Factory worker" = "9", "Household help" = "10", "Transport related work" = "11", "Own business" = "12", "Service Work (NGO, gov,etc.)" = "13", "NREGA" = "14", "Housewife" = "15", "Other" = "16")) +
  coord_flip()

labels <- c("Agricultural wage worker", "Livestock worker", "Farmer", "Casual labor", "Construction/brick labor", "Gleaning/foraging", "Fisherman", "Fishery worker", "Factory worker", "Household help", "Transport related work", "Own business", "Service Work (NGO, gov,etc.)", "NREGA", "Housewife", "Other")

```



## HH Secondary Occupation 

````{r}
soccup1 <- baseline %>% 
  filter(relationship1 == 1) %>%
  select(c(village = "village", job = "job1_1"))
soccup2 <- baseline %>% 
  filter(relationship2 == 1) %>%
  select(c(village = "village", job = "job1_2"))
soccup3 <- baseline %>% 
  filter(relationship3 == 1) %>%
  select(c(village = "village", job = "job1_3"))
soccup4 <- baseline %>% 
  filter(relationship4 == 1) %>%
  select(c(village = "village", job = "job1_4")) 


soccup1 = na.omit(occup1)
soccup2 = na.omit(occup2)
soccup3 = na.omit(occup3)
soccup4 = na.omit(occup4)

soccup <- rbind(occup1, occup2, occup3, occup4)
```

```{r}
ggplot(soccup, aes(x = job)) +
  geom_histogram() 
```



## HH Age 
	
	
	
##HH education 
	
	
	
##HH Marital status 
	



##Number of married women per household 
	
	
	

	
	
	
	
##Savings 
	
```{r}

```

-------------------------
##Appendix 


Primary Occupation for all  
 

toccup1 <- baseline %>% 
  filter(job1_1 != 0) %>%
  select(c(village = "village", job = "job1_1"))
toccup2 <- baseline %>% 
  select(c(village = "village", job = "job1_2"))
toccup3 <- baseline %>% 
  select(c(village = "village", job = "job1_3"))
toccup4 <- baseline %>% 
  select(c(village = "village", job = "job1_4")) 

toccup5 <- baseline %>% 
  select(c(village = "village", job = "job1_5"))
toccup6 <- baseline %>% 
  select(c(village = "village", job = "job1_6"))
toccup7 <- baseline %>% 
  select(c(village = "village", job = "job1_7"))
#toccup8 <- baseline %>% 
  #select(c(village = "village", job = "job1_8")) 

toccup9 <- baseline %>% 
  select(c(village = "village", job = "job1_9"))
#toccup10 <- baseline %>% 
  #select(c(village = "village", job = "job1_10"))
#toccup11 <- baseline %>% 
 # select(c(village = "village", job = "job1_11"))
toccup12 <- baseline %>% 
  select(c(village = "village", job = "job1_12")) 
  
toccup1 = na.omit(toccup1)
toccup2 = na.omit(toccup2)
toccup3 = na.omit(toccup3)
toccup4 = na.omit(toccup4)
toccup5 = na.omit(toccup5)
toccup6 = na.omit(toccup6)
toccup7 = na.omit(toccup7)
#toccup8 = na.omit(occup8)
toccup9 = na.omit(toccup9)
#toccup10 = na.omit(occup10)
#toccup11 = na.omit(occup11)
toccup12 = na.omit(toccup12)

toccup <- rbind(toccup1, toccup2, toccup3, toccup4, toccup5, toccup6, toccup7, toccup9, toccup12)



#Secondary Occupation for all  

stoccup1 <- baseline %>% 
  filter(job1_1 != 0) %>%
  select(c(village = "village", job = "job2_1"))
stoccup2 <- baseline %>% 
  select(c(village = "village", job = "job2_2"))
stoccup3 <- baseline %>% 
  select(c(village = "village", job = "job2_3"))
stoccup4 <- baseline %>% 
  select(c(village = "village", job = "job2_4")) 

stoccup5 <- baseline %>% 
  select(c(village = "village", job = "job2_5"))
stoccup6 <- baseline %>% 
  select(c(village = "village", job = "job2_6"))
stoccup7 <- baseline %>% 
  select(c(village = "village", job = "job2_7"))
#toccup8 <- baseline %>% 
  #select(c(village = "village", job = "job1_8")) 

stoccup9 <- baseline %>% 
  select(c(village = "village", job = "job2_9"))
#toccup10 <- baseline %>% 
  #select(c(village = "village", job = "job1_10"))
#toccup11 <- baseline %>% 
 # select(c(village = "village", job = "job1_11"))
stoccup12 <- baseline %>% 
  select(c(village = "village", job = "job2_12")) 
  
stoccup1 = na.omit(stoccup1)
stoccup2 = na.omit(stoccup2)
stoccup3 = na.omit(stoccup3)
stoccup4 = na.omit(stoccup4)
stoccup5 = na.omit(stoccup5)
stoccup6 = na.omit(stoccup6)
stoccup7 = na.omit(stoccup7)
#toccup8 = na.omit(occup8)
stoccup9 = na.omit(stoccup9)
#toccup10 = na.omit(occup10)
#toccup11 = na.omit(occup11)
stoccup12 = na.omit(stoccup12)

stoccup <- rbind(stoccup1, stoccup2, stoccup3, stoccup4, stoccup5, stoccup6, stoccup7, stoccup9, stoccup12)





